Test susieI using chr17 to 22

### 2020-08-19 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
susieI

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
tag <- '20200813-1-1'
```

# MR.ASH for genes only

pip distribution

```{r rpip 1, fig.height=4, fig.width=10}
chrom = 17
rpipf <- paste0(outputdir, tag, "-mr.ash.rPIP.txt")
allchr <- read.table(rpipf, header = T)
a <- allchr[allchr["chrom"]==chrom,]
print(paste("plot for chr", chrom))
par(mar=c(5, 4, 4, 6) + 0.1)
with(a, plot(p0, rPIP, col ='salmon', xlab = "position", ylab= "Sum of PIP", type = 'h', lwd = 2))
par(new = T)
with(a, plot(p0, nCausal, pch =19, col = "darkgreen",axes = FALSE, bty = "n", xlab = "", ylab = ""))
axis(side = 4)
mtext(side = 4, line = 3, 'No. causal signals')
legend("topleft",
       legend=c("Mr.ASH PIP", "# Causal"),
       lty=c(1,0), pch=c(NA, 19), col=c("salmon", "darkgreen"))
grid()
```

```{r rpip 1, fig.height=4, fig.width=10}
 hist(a$rPIP, breaks = 100, col = "salmon", xlab = "PIP", main = "PIP distribution")
```

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
susiedir <- "~/causalTWAS/simulations/simulation_susieI_20200813/"
tag <- '20200813-1-1'
Niter <- 10
```

# MR.ASH pip distribution

* Use mr.ash for gene only:

```{r rpip 1, fig.height=6, fig.width=6}
rpipf <- paste0(outputdir, tag, "-mr.ash.rPIP.txt")

a <- read.table(rpipf, header = T)
a.c <- a[a$nCausal > 0, ]
ax <- pretty(0:max(a$rPIP), n = 30)

par(mfrow=c(2,1))
h1 <- hist(a$rPIP, breaks = 100, xlab = "PIP", main = "PIP distribution-all", col = "grey"); grid()
h2 <- hist(a.c$rPIP, breaks = h1$breaks, xlab = "PIP", main = "PIP distribution-causal", col = "salmon");grid()
```

* MR.ash2s results for the same simulated data

```{r rpip 2, fig.height=6, fig.width=6}
rpipf <- "~/causalTWAS/simulations/simulation_ashtest_20200721/20200721-1-1-mr.ash2s.lassoes-es.rPIP.txt"

a <- read.table(rpipf, header = T)
a.c <- a[a$nCausal > 0 ,]
ax <- pretty(0:max(a$rPIP), n = 30) # Make a neat vector for the breakpoints

par(mfrow=c(2,1))
h1 <- hist(a$rPIP, breaks = 100, xlab = "PIP", main = "PIP distribution-all", col = "grey"); grid()
h2 <- hist(a.c$rPIP, breaks = h1$breaks, xlab = "PIP", main = "PIP distribution-causal", col = "salmon");grid()
```

# susieI genes

Regions: We use regional PIP of both SNP and gene from mr.ash2s > 0.3 , and also require at least one causal gene or SNP is present, also, at least one gene.

Prior change for each iteration:
```{r iter}
load(paste0(outputdir, tag, ".susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

Results for each region:
```{r regions}
regionlist <- readRDS(paste0(outputdir, tag, "_regionlist.rds"))
ng <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene", , drop = F ])[1]))
ng.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene" & x$ifcausal == 1, , drop = F])[1]))
ns.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP" & x$ifcausal == 1, , drop = F])[1]))
ngdf <- data.frame("ngene" = ng, "ncausalgene" = ng.c, "ncausalSNP" = ns.c)
for (i in Niter){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(gene.rpiplist)
}
ngdf
```

# susieI shuffle genes
Shuffle genes to different regions.

Prior change for each iteration:
```{r iter shuffle}
tag <- '20200813-1-1-shuffleg'
load(paste0(outputdir, tag, ".susieIres.Rd"))
df <- cbind(prior.gene_rec, prior.SNP_rec)
rownames(df) <- paste("Iteration", 1:Niter)
colnames(df) <- c("Prior.gene", "Prior.SNP")
df
```

Results for each region:
```{r regions shuffle}
regionlist <- readRDS(paste0(outputdir, tag, "_regionlist.rds"))
ng <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene", , drop = F ])[1]))
ng.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "gene" & x$ifcausal == 1, , drop = F])[1]))
ns.c <- unlist(lapply(lapply(regionlist, '[[', "anno"), function(x) dim(x[x$type == "SNP" & x$ifcausal == 1, , drop = F])[1]))
ngdf <- data.frame("ngene" = ng, "ncausalgene" = ng.c, "ncausalSNP" = ns.c)
for (i in 1:Niter){
  resf <- paste0(outputdir, tag, ".", i, ".susieIres.Rd") 
  load(resf)
  ngdf[, paste("Prior.gene", i)] <- unlist(gene.rpiplist)
}
ngdf
```
